### 2015-05-15 whoop.tex
added page in book and slight rewording

Another limitation of \whoop is that it is unable to verify drivers designed to be accessed by only a single process at a time. This \emph{single-open device}~\cite[p.\ 173]{corbet2005linux} mode can be enforced by atomically testing (at the beginning of an entry point) a flag that indicates device availability: if the flag is set to true, then the checking entry point executes, else it blocks. Because \whoop performs pair-wise analysis, it over-approximates this flag, and thus can falsely report a pair as racy. However,~\cite{corbet2005linux} advises against serializing drivers in this way, as it hinders user ingenuity (e.g.\ a user might expect that a device can be accessed concurrently for performance).

>>>>

Another limitation of \whoop is that it is unable to verify drivers designed to be accessed by only a single process at a time. This \emph{single-open device}~\cite[p.\ 173]{corbet2005linux} mode can be enforced by atomically testing (at the beginning of an entry point) a global flag that indicates device availability: if the flag is set to true, then the checking entry point executes, else it blocks. Because \whoop over-approximates read accesses to shared variables, and thus this flag, it can falsely report a pair as racy. However,~\cite[p.\ 173]{corbet2005linux} advises against serializing drivers in this way, as it hinders user ingenuity (e.g.\ a user might expect that a device can be accessed concurrently for performance).
